Algorithms for Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2014-10-14 paper/paper.tex
replies to review comments

This paper is an extension of our earlier conference
publication~\cite{Malawski-SC12}.
Here we present a more detailed performance evaluation, including the discussion
of results based on varying deadline and budget constraints. We also report on new
results and discussion of task granularity in the context of the resource
billing cycle, which is an important aspect of scheduling and resource provisioning
on cloud infrastructures.

@@

@@

In this experiment the actual runtime of each task is adjusted in the
simulation by adding a random error to the estimated runtime of $\pm p\%$.
Since the sampling is done uniformly, we expect to get just as many
overestimates as underestimates in any given simulation.

>>>>

This paper is an extension of our earlier conference
publication~\cite{Malawski-SC12}.
Here we present a more detailed performance evaluation, including the discussion
of results based on varying deadline and budget constraints. We also report on new
results and discussion of task granularity in the context of the resource
billing cycle, which is an important aspect of scheduling and resource provisioning
on cloud infrastructures. The section on the related work and the examples of algorithms 
have been also extended to provide a better positioning and increase the readability of the paper.

@@

The decision to use a simulator instead of actual execution of workflows on clouds 
was motivated by our intention to perform an extensive analysis of the algorithms
in various aspects. This results in a large parameter space, since e.g. for analysis 
presented in Section~\ref{sec:variances}, we needed to execute 525,000 simulations 
of workflow ensembles, each ensemble consisting of 50 workflows of up to 1000 tasks.
Not only would this be impractical to run on a real infrastructure for obvious reasons, 
but also it would not allow to study such interesting aspects as the influence 
of task graularity presented in Section~\ref{sec:granularity}. 
The usage of simulator, although also quite compute intensive, allowed us
to study all these aspects in detail.

@@

In this experiment the actual runtime of each task is adjusted in the
simulation by adding a random error to the estimated runtime of $\pm p\%$.
Since the sampling is done uniformly, we expect to get just as many
overestimates as underestimates in any given simulation. 
Our approach for generating errors is similar to the one used in~\cite{Zheng2013b},
where the random error represents the Quality of Estimation metric.
